### 2021-04-15 input/proposal.tex
abstract reworkd

\begin{proof}
  % \begin{asparadesc}
  % \item [$BEF \implies CP$:]
  When a \process $s_1$ becomes a source, it belongs to its own
  partition, for there exists no better partition than its own:
  $\forall p \in V: |\Pi_{s_1 s_1}| < |\Pi_{s_1 p}|$. It delivers,
  hence forwards such $\alpha$ message to its -- current or future --
  neighbors. Since communication links are reliable, neighboring
  \processes eventually receive such notification $\forall \langle
  s_1, q \rangle \in E, s_1 \in S \iff \eventually
  r_q(\alpha_{s_1}^{w_{s_1 q}})$. Most importantly, whatever the order
  of received messages, every \process $q'$ in this neighborhood --
  such that there exists no better partition $s_2$ than the received
  one -- delivers and forwards it: $\forall s_2 \in S: |\Pi_{q' s_1}|
  < |\Pi_{q' s_2}| \implies \eventually d_{q'}(\alpha_{s_1}^{w_{s_1
      q'}})$. By transitivity, the message originating from $s_1$
  transitively reaches all such \processes through their shortest
  paths: $\forall q'' \in V, s_1, s_2 \in S: |\Pi_{q'' s_1}| <
  |\Pi_{q'' s_2}| \implies \eventually d_{q''}(\alpha_{s_1}^{|\Pi_{s_1
      q''}|})$.  Since there exists only one best sum of weights per
  \process that can never be retracted, \processes eventually reach
  consistent partitioning.
  %% /!\ not equivalence for there exists other implementations.
  %% \item [$CP \implies BEF$:] By contradiction, if a \process $q \in
  %%   \Pi_{sp} = [s, \ldots, q, q', \ldots, p]$ with $s, q, p \in P_s$
  %%   does not forward its received $\alpha_s^{|\Pi_{sq}|}$, then
  %%   following \processes from $q'$ to $p$ may mistake another
  %%   partition for their  because it needs the weight $W_{pq}$.
  %% \end{asparadesc}
\end{proof}

@@

\begin{proof}
  \Processes deliver and forward the best sum of weights they
  received. The only case where a \process would block such epidemic
  propagation would be when it received and delivered a message from a
  partition that has since then been deleted but with a better sum of
  weights than newly received ones. Removing \emph{forever} all such
  stale messages about deleted partitions would allow \processes to
  propagate their best up-to-date partition again, eventually reaching
  consistent partition together.
\end{proof}

@@

>>>>

\begin{proof}
  % \begin{asparadesc}
  % \item [$BEF \implies CP$:]
  When a \process $s_1$ becomes a source, it belongs to its own
  partition, for there exists no better partition than its own:
  $\forall p \in V: |\Pi_{s_1 s_1}| < |\Pi_{s_1 p}|$. It delivers,
  hence forwards such $\alpha$ message to its -- current or future --
  neighbors. Since communication links are reliable, neighboring
  \processes eventually receive such notification $\forall \langle
  s_1, q \rangle \in E, s_1 \in S \iff \eventually
  r_q(\alpha_{s_1}^{w_{s_1 q}})$. Most importantly, whatever the order
  of received messages, every \process $q'$ in this neighborhood --
  such that there exists no better partition $s_2$ than the received
  one -- delivers and forwards it: $\forall s_2 \in S: |\Pi_{q' s_1}|
  < |\Pi_{q' s_2}| \implies \eventually d_{q'}(\alpha_{s_1}^{w_{s_1
      q'}})$. By transitivity, the message originating from $s_1$
  reaches all such \processes through their shortest paths: $\forall
  q'' \in V, s_1, s_2 \in S: |\Pi_{q'' s_1}| < |\Pi_{q'' s_2}|
  \implies \eventually d_{q''}(\alpha_{s_1}^{|\Pi_{s_1 q''}|})$.
  Since there exists only one best sum of weights per \process that
  can never be retracted, \processes eventually reach consistent
  partitioning.
  %% /!\ not equivalence for there exists other implementations.
  %% \item [$CP \implies BEF$:] By contradiction, if a \process $q \in
  %%   \Pi_{sp} = [s, \ldots, q, q', \ldots, p]$ with $s, q, p \in P_s$
  %%   does not forward its received $\alpha_s^{|\Pi_{sq}|}$, then
  %%   following \processes from $q'$ to $p$ may mistake another
  %%   partition for their  because it needs the weight $W_{pq}$.
  %% \end{asparadesc}
\end{proof}

@@

\begin{proof}
  \Processes deliver and forward the best sum of weights they
  received. The only case where a \process would block such epidemic
  propagation would be when it received and delivered a message from a
  partition that has since then been deleted but with a better sum of
  weights than newly received ones. Removing \emph{forever} all such
  stale messages about deleted partitions would allow \processes to
  propagate their best up-to-date partition again, eventually reaching
  consistent partitioning together.
\end{proof}

@@

\vfill

\TODO{spacing}

\newpage
